Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-23 doc/manuscript/ESSDmanuscript.Rmd
reinstate removal of NAs from table

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes<-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks

>>>>

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE, message = FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes <-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks
